---
title: "Ikea Dataset Final Project: EPI 590R"
author: "Victoria Ngo "
date: '2024-09-04'
format: html
echo: false
---

**Data set: IKEA Saudi Arabian Furniture 2020 Catalog**

This data set was web scraped from the IKEA Saudi Arabian website for the furniture category on April 20, 2020. This was featured by the TidyTuesday data set repository on November 11, 2020 (tidytuesday/data/2020/2020-11-03). This data set contains information on the furniture items name, category, price, online availability, web link, colors available, depth, width, height, designer, and a short description of each item.

```{r}
#| warning: false
#| message: false

#loading packages
library(tidyverse)
library(gtsummary)
library(here)
```

```{r}
#loading in dataset using here::here
ikea <- read.csv(here::here("data", "ikea.csv"))
```

**GT Summary table**

```{r}
#| label: tbl-one
#| tbl-cap: "Table of descriptive statistics for Items Sold Online"
tbl1<-tbl_summary(
	ikea,
	by = sellable_online,
	include = c(category, other_colors),
label = list(
	category ~"Furniture Category",
	other_colors ~"Other Colors Sold"),
) |>
	bold_labels()
tbl1
#in line texts
total_items <- nrow(ikea)
inline_online_colors<-inline_text(tbl1, variable = other_colors,column = "True")
```

There were a total of `r total_items` furniture items in the 2020 Saudi Arabian IKEA catalog. Of the `r total_items` available items, `r inline_online_colors` of the items had alternate colors and were able to be sold online.

**Regression Table**

```{r}
#| label: tbl-two
#| tbl-cap: "Univariate Regression Table"
tbl_uvregression(
	ikea,
	y = price,
	include = c(category, sellable_online, other_colors, height, depth, width),
	method = lm,
	label = list(
		category ~"Furniture Category",
		other_colors ~"Other Colors Sold",
		sellable_online ~"Sellable Online",
  	height ~"Height in cm",
  	depth ~"Depth in cm",
  	width ~"Width in cm"),
) |>
	bold_labels()
```

**Data figure: Basic histogram with custom titles and labels**

```{r}
#| label: fig-hist
#| fig-cap: "Histogram of IKEA Furniture Width"
#| message: false
hist(ikea$width,
		 main = "Distribution of IKEA Furniture Width",  # Title of the histogram
		 xlab = "Width (in cm)",                         # X-axis label
		 ylab = "Frequency",                             # Y-axis label
		 col = "#1E90FF",                                   # Color of the bars
		 border = "black")                               # Color of the bar borders
png(filename = here("Figure","ikeawidthdistr.png"))
dev.off()
```

@tbl-one displays descriptive statistics for this data set, @tbl-two displays the univariate regression table, and @fig-hist displays a histogram of the furniture widths.
